Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-02-24 doc/PRF2022/PRF_main.tex
edits

To perform a single time step, we
(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
(ii) compute the force and torque~\eqref{eq:FandTdef},
and finally (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
The velocities $(\vv_i, \omega_i)$ obtained
from~\eqref{eq:rigid-vel} are used to update the
particle positions and orientations
using the second-order Adams-Bashforth scheme.

@@

Figure~\ref{fig:relax} shows the steady state in a quiescent flow.
Three distinct phases emerge. For Type I, amphiphiles,
the tail interactions are attractive, and particles collectively
form multiple domains of bilayers (Figure~\ref{fig:relax}(b)).
We refer to this as the ``bilayer'' phase.

>>>>

To perform a single time step, we
(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
(ii) compute the force and torque~\eqref{eq:FandTdef},
and finally (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
The velocities $(\vv_i, \omega_i)$ obtained
from~\eqref{eq:rigid-vel} are used to update the
particle positions and orientations
using the second-order Adams-Bashforth scheme
with time step size $\Delta t.$

@@

Figure~\ref{fig:relax} shows the steady state in a quiescent flow.
Three distinct phases emerge. For Type I, amphiphiles,
the tail interactions are attractive, and particles collectively
form disjoint bilayer components (Figure~\ref{fig:relax}(b)).
We refer to this as the ``bilayer'' phase.
